Competing Bandits

### 2018-08-10 paper/competing_bandits.tex
update figures in the paper to include confidence intervals and use the same data
further updates to figures

\begin{figure}
\caption{Reputation Trajectories in Isolation}
\includegraphics[scale=0.2]{"figures/Reputation Trajectory for Heavy Tail 10 arms"}
\includegraphics[scale=0.2]{"figures/Reputation Trajectory for Needle In Haystack High 10 arms"}
\label{prelim_means}
\caption*{\tiny{The plots contain the average reputation over $250$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. TODO: get rid of smoothing on plot}}
\end{figure}

@@

\begin{figure}
\label{rel_rep_ht_fine}
\caption{Relative Reputation - Heavy Tail}
\includegraphics[scale=0.3]{figures/ts_dg_heavy_fine}
\caption*{TODO: Reduce the range of the x-axis of this so that you can understand when TS starts to do better than DG}
\end{figure}

>>>>

\begin{figure}
\caption{Mean Reputation Trajectories in Isolation}
\includegraphics[scale=0.2]{"figures/heavy_tail_iso_mean"}
\includegraphics[scale=0.2]{"figures/nih_iso_mean"}
\label{prelim_means}
\caption*{\tiny{The plots contain the average reputation over $250$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. TODO: get rid of smoothing on plot}}
\end{figure}

@@
